Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
acknowledgements

We have developed an application, that we named {\em Kimbee}, that aims to help the process of speech therapy in young children. Speech therapies are often expensive for schools and parents to maintain, especially with younger children who require more time than others. Our application does not replace the speech therapist, rather it supplements the therapy. Instead of being limited to short sessions, therapists can use {\em Kimbee} to have their students work at home as well as in the classroom. The therapist can then monitor the child's progress through our application and use this newly gained information to further tailor the therapy to individual students. This will save both time and money for school districts and parents who are paying for their child's therapy.

@@

>>>>

We have developed an application named {\em Kimbee} that aims to help the process of speech therapy in young children. Speech therapies are often expensive for schools and parents to maintain, especially with younger children who require more time than others. Our application does not replace the speech therapist, rather it supplements the therapy. Instead of being limited to short sessions, therapists can use {\em Kimbee} to have their students work at home as well as in the classroom. The therapist can then monitor the child's progress through our application and use this newly gained information to further tailor the therapy to individual students. This will save both time and money for school districts and parents who are paying for their child's therapy.

@@

We'd like to thank Richard Kreider of the Arlington Public School District for meeting with us to discuss the viability and details of our project when it was in its developing stages and then again to discuss improvements when Kimbee was almost finished.
